The effects of drought on land cover change and vegetation productivity in continental Chile

### 2024-05-08 article/paper_drought_Chile2023.qmd
actualizar local servidor

```{r fig-varImportance}
#| echo: false
#| fig-pos: "!ht"
#| fig-cap: "cdcdcdc"
#| fig-width: 3
#| out-width: ".01\\textwidth"
knitr::include_graphics("../output/figs/bars_relative_importance_RF.png")
```

>>>>

```{r fig-varImportance}
#| echo: false
#| fig-pos: "!ht"
#| fig-cap: "cdcdcdc"
#| out-width: "\\textwidth"
knitr::include_graphics("../output/figs/bars_relative_importance_RF.png")
```
